Modeling and Simulation of Load Balancing Strategies for Computing in High Energy Physics

### 2018-10-09 paper/paper.tex
Add missing word

\abstract{%
	The amount of data to be processed by experiments in high energy physics (HEP) is tremendously increasing in the coming years. To cope with this increasing load, most efficient usage of the resources is mandatory. Furthermore, the computing resources for user jobs in HEP will be increasingly distributed and heterogeneous, resulting in more difficult scheduling due the increasing complexity of the system.
	We aim to create a simulation for the WLCG helping the HEP community to solve both challenges: a more efficient utilization of the grid and coping with the rising complexity of the system.
	There is currently no simulation existing helping the operators of the grid to make the correct decisions while optimizing the load balancing strategy.

>>>>

\abstract{%
	The amount of data to be processed by experiments in high energy physics (HEP) is tremendously increasing in the coming years. To cope with this increasing load, most efficient usage of the resources is mandatory. Furthermore, the computing resources for user jobs in HEP will be increasingly distributed and heterogeneous, resulting in more difficult scheduling due to the increasing complexity of the system.
	We aim to create a simulation for the WLCG helping the HEP community to solve both challenges: a more efficient utilization of the grid and coping with the rising complexity of the system.
	There is currently no simulation existing helping the operators of the grid to make the correct decisions while optimizing the load balancing strategy.
